Reduced diversity and increased specialization of Alaska salmon fishermen:

### 2016-10-28 salmon/paper/salmon_paper_appendix.Rmd
appendix update

# Also load in raw CFEC data for plots
cfec <- feather::read_feather("../../portfolio/data-generated/salmon.feather")
cfec = cfec[cfec$p_fshy%in%c("S 01A", "S 01E", "S 01K", "S 03A", "S 03E", "S 01M"),]
cfec$year = as.numeric(substr(cfec$landdate, 1, 4))

@@

@@

## Species composition

```{r, fig.cap="Proportion of species landed, weighted by earnings", fig.pos="placeHere", echo=FALSE, fig.height = 3.3}
# plot proportion of species landed by salmon permit
group_by(cfec.raw[cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p)) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() + facet_wrap(~p_fshy) + 
  ylab("Species % (total) ") + xlab("")
```

>>>>

# Also load in raw CFEC data for plots
#cfec <- feather::read_feather("../../portfolio/data-generated/salmon.feather")
cfec = readRDS("../../portfolio/data-generated/salmon_data_for_paper.rds")
cfec = cfec[cfec$p_fshy%in%c("S 01A", "S 01E", "S 01K", "S 03A", "S 03E", "S 01M"),]
cfec$year = as.numeric(substr(cfec$landdate, 1, 4))

@@

# summarize annual data - total revenue and CV (3-year rolling)
annual_summary = group_by(cfec[which(cfec$year>0),], year, p_fshy) %>% 
  summarize(tot = sum(g_earn)) %>% arrange(p_fshy) %>% 
  group_by(p_fshy) %>% mutate(rollmean = c(NA,rollmean(tot,k=3),NA),
    rollsd = c(NA,rollapply(tot,width=3,sd),NA), rollcv = rollsd/rollmean)
#ggplot(annual_summary, aes(year, rollcv,color=p_fshy)) + geom_line()
#ggplot(annual_summary, aes(log(rollmean), rollcv, color=p_fshy)) + geom_point()

# calculate total earnings by person / permit / year
indiv_summary = group_by(cfec[which(cfec$year>0),], year, p_holder) %>% 
  mutate(n = length(unique(p_fshy))) %>% filter(n == 1) %>% 
  group_by(year, p_holder) %>% 
  summarize(g = sum(g_earn), p_fshy = p_fshy[1])
# add in missing data
people_year = expand.grid("year"=unique(cfec$year[cfec$year>0]), "p_holder"=unique(indiv_summary$p_holder))
indiv_summary = left_join(people_year, indiv_summary)
# apply rolling mean / sd to data
indiv_summary = group_by(indiv_summary, p_holder) %>% 
  mutate(rollmean = c(NA,rollapply(g,width=3,mean),NA),
    rollsd = c(NA,rollapply(g,width=3,sd),NA),
    rollcv = rollsd/rollmean)
# calculate averages across individuals over time
indiv_summary = group_by(indiv_summary, p_fshy, year) %>% 
  summarize(ind_mean = mean(rollmean,na.rm=T), 
    ind_cv = mean(rollcv,na.rm=T))

alldat = left_join(annual_summary, indiv_summary)
# this shows cvs that individuals experience are same as cvs of aggregate
#ggplot(alldat, aes(rollcv, ind_cv,color=p_fshy)) + geom_point()
#ggplot(alldat, aes(log(rollmean), ind_cv,color=p_fshy)) + geom_point()
#ggplot(alldat, aes(log(rollmean),log(ind_mean), color=p_fshy)) + geom_point(aes(alpha=year))
#ggplot(alldat, aes(year, log(rollmean))) + facet_wrap(~p_fshy) + geom_line()
#ggplot(alldat, aes(year, rollcv)) + facet_wrap(~p_fshy) + geom_line() + geom_line(aes(year, ind_cv, color="red"))
#ggplot(alldat, aes(year, log(ind_cv/rollcv), col=p_fshy)) + geom_line()
#ggplot(alldat, aes(log(rollcv), log(ind_cv),color=p_fshy)) + geom_point()

@@

## Species diversity

```{r, fig.cap="Proportion of species landed, weighted by earnings", fig.pos="placeHere", echo=FALSE, fig.height = 3.3, eval=FALSE}
## Species composition
# plot proportion of species landed by salmon permit
group_by(cfec.raw[cfec.raw$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p)) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() + facet_wrap(~p_fshy) + 
  ylab("Species % (total) ") + xlab("")
```
